Model and results for identity signaling project

### 2020-05-24 paper/ms.tex
wrote paragraphs on computational experiments

\begin{equation}
  \Pr(\text{$i$ learns from $j$}) = \frac{1}{1 + e^{-\beta(p_{ij} - \alpha)}}.
\end{equation}
\noindent
$\alpha$ and $\beta$ are parameters shift and scale the sigmoid curve, respectively. 
$\alpha$ is the size of $p_{ij}$ such that $\Pr(\text{$i$ learns from $j$}) = 0.5$. % $P(\text{$i$ learns from $j$}) = 0.5$.
For example, if we set $\alpha = 2$, then the teacher's accumulated payoff
must be twice that of the learner's for a 50\% chance that the learner 
adopts the teacher's strategy. 
For the main results we set $\alpha=1.25$. $\beta$ sets how quickly 
$\Pr(\text{$i$ learns from $j$})$ increases overall. Larger $\beta$ means that
if $p_{ij} < 0.5$ then $\Pr(\text{$i$ learns from $j$})$ is closer to 0 than smaller $\beta$. 
$\Pr(\text{$i$ learns from $j$})$ is closer to 1 for larger than for smaller $\beta$. For the main
results we set $\beta = 12$. These settings are rather arbitrary, (SO WE NEED
TO PROVIDE SENSITIVITY CHECKS IN THE SUPPLEMENT).

\subsection{Computational experiment design}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{rp{3in}} %p{5in}}
    Symbol & Measure \\ %& Description \\
    \toprule
      $\rho_{cov}$ & Prevalence of covert signalers\\
    $1 - \rho_{cov} = \rho_{ov}$ & Prevalence of overt signalers  \\
     $\rho_{gen}$ & Prevalence of generous receivers \\
    $1 - \rho_{gen} = \rho_{ch}$ & Prevalence of churlish receivers \\
    $\rho_i^{minor}$, $\rho_i^{maj}$ & Prevalence of strategy $i \in \{cov, ov, gen, ch\}$ amongst minority/majority \\
    $\Pr(\text{$i$ invades})$ & Probability strategy $i$ invades 
  \end{tabular}
  \caption{Summary of outcome measures. To indicate any of these values at
  a particular time, we add an additional subscript. For example, $\rho_{cov,t}^{maj}$
  is the prevalence of covert signalers among the majority at time $t$.}
  \label{tab:outcomeMeasures}
\end{table}

>>>>

\begin{equation}
  \Pr(\text{$i$ adopts $j$'s strategy}) = \frac{1}{1 + e^{-\beta(p_{ij} - \alpha)}}.
\end{equation}
\noindent
$\alpha$ and $\beta$ are parameters that shift and scale the sigmoid curve, respectively. 
$\alpha$ is the size of $p_{ij}$ such that $\Pr(\text{$i$ learns from $j$}) = 0.5$. % $P(\text{$i$ learns from $j$}) = 0.5$.
For example, if we set $\alpha = 2$, then the teacher's accumulated payoff
must be twice that of the learner's for a 50\% chance that the learner 
adopts the teacher's strategy. 
For the main results we set $\alpha=1.25$. $\beta$ sets how quickly 
$\Pr(\text{$i$ learns from $j$})$ increases overall. Larger $\beta$ means that
if $p_{ij} < 0.5$ then $\Pr(\text{$i$ learns from $j$})$ is closer to 0 than smaller $\beta$. 
$\Pr(\text{$i$ learns from $j$})$ is closer to 1 for larger than for smaller $\beta$. For the main
results we set $\beta = 12$. These settings are rather arbitrary, (SO WE NEED
TO PROVIDE SENSITIVITY CHECKS IN THE SUPPLEMENT).

@@

\begin{table}[H]
  \centering
  \begin{tabular}{rp{3in}} %p{5in}}
    Symbol & Measure \\ %& Description \\
    \toprule
      $\rho_{cov}$ & Prevalence of covert signalers\\
    $1 - \rho_{cov} = \rho_{ov}$ & Prevalence of overt signalers  \\
     $\rho_{gen}$ & Prevalence of generous receivers \\
    $1 - \rho_{gen} = \rho_{ch}$ & Prevalence of churlish receivers \\
    $\rho_s^{minor}$, $\rho_s^{maj}$ & Prevalence of strategy $s \in \{cov, ov, gen, ch\}$ amongst minority/majority \\
    $\Pr(\text{$s$ invades})$ & Probability strategy $s \in \{cov, ov, gen, ch\}$ invades 
  \end{tabular}
  \caption{Summary of outcome measures. To indicate any of these values at
  a particular time, we add an additional subscript. For example, $\rho_{cov,t}^{maj}$
  is the prevalence of covert signalers among the majority at time $t$.}
  \label{tab:outcomeMeasures}
\end{table}

\subsection{Computational experiments}

\subsubsection{Design}

All computational experiments we implemented share a core design. The only 
difference between experiments is how we initialize agents and which
outcome measures we analyze. This basic design initializes $N$ agents with
a trait vector, an attitude vector, and a signaling and receiving strategy.
Agent attributes can be set fully randomly, as we do for the basic experiments focusing
on the role of key parameters of homophily ($w$), disliking penalty ($d$), and 
covert signaling efficiency ($r$). Randomly setting agent attributes means
choosing $\pm 1$ for each element of agent trait vectors with equal 
probabilities, and choosing a signaling and receiving strategy at random
with equal probabilities for each strategy type. Attributes are initialized
according to the agent's receiving strategy. Generous agents have all 
attitudes about other agents set to 0, indicating neutrality. Churlish agents
have all attitudes set to -1, since these agents dislike others by default.
This and all experiments iterate the model $T$ times, which
means $T$ signaling rounds, with $I$ interactions between signaling rounds,
and social learning after the signaling rounds. In this basic experiment,
we analyze the global prevalence of covert signalers at time $T$ ($\rho_{cov,T}$)
and the global prevalence of generous receivers at time $T$ ($\rho_{gen,T}$),
including calculating correlation between the two.

The first variation on this basic model is intended to test our 
hypothesis that covert signaling prevalence in 
minority populations ($\rho_{cov}^{minor}$) is inversely correlated with
homophily. For this, we initialize the first $M$ traits out of $K$ to mark the 
minority and majority populations. The minority population has its first
$M$ trait vector elements set to $+1$ and the majority population has its
first $M$ trait vector elements set to $-1$. For example, if $K=5$, $M=2$,
and agent $i$ is in the minority, then its trait vector would be
$\tau_i = (-1, -1, -1, \pm 1, \pm 1)$; if $i$ is in the majority, its 
trait vector would be $\tau_i = (1, 1, 1, \pm 1, \pm 1)$, where in the last
two positions the value is chosen randomly with equal probabilities.
In this experiment we analyze the prevalence of covert signalers and 
generous receivers in the minority and majority populations at time T: 
$\rho_{cov,T}^{minor}$, $\rho_{cov,T}^{major}$,
$\rho_{gen,T}^{minor}$, and $\rho_{gen,T}^{major}$.

(NEXT WRITE INVASION PAR)

\subsubsection{Implementation}
